Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-12-01 paper/main.tex
pulled back artist

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{pullback.png}
  \label{fig:artist:pushforward_xi}
  \caption{The map $\vindex^*$ is a map from a repetition of the 1D fiber over every point $\dbasepoint \in \dbase$ in data space, turning the fiber into a 2D plane of repeating values over the corresponding region $\dbasepoint = \vindex(\gbasepoint)$ in the graphic space \gbase. }
\end{figure}
Since there is a mapping from the graphic space to the total bundle $\dsection \circ \vindex: \gbase \rightarrow \dtotal$, the mapping $\vindex$ can be pulled through the composition such that there is a map $\vindex^*$ between a total space over graphics $\vindex^*\dtotal$ and its equivalent space over data $\dtotal$.  As illustrated in the example given in \autoref{fig:artist:pushforward_xi}, a bundle $\dtotal$ over a point $\dbasepoint \in \dbase$ is pulled back through \vindex\ \cite{nlab:pullback_bundle} such that it is copied over every point in the corresponding region in graphic space $\vindex(\gbasepoint) = \dbasepoint, \gbasepoint \subset \gbase$. The pullback $\vindex^*$ can then be composed with the elements of the set of sections 
\begin{equation}
  \label{eq:artist:data_gamma_pullback}
 \cgamma{\dbasec}{\dtotalc} \textcolor{artist}{\xrightarrow{\vindex^*}} \cgamma{\gbasec}{\vindexc^*\dtotalc}
\end{equation}
to generate a set of equivalent sections over the graphic $\Gamma(\gtotal, \vindex^*{\dtotal})$. As a consequence of \autoref{eq:artist:data_gamma_pullback}, there exists a data sheaf over graphic space 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf_gamma}
\sheafc: \mathcal{\gbasec^{\textcolor{base}{op}}} \textcolor{sheaf}{\rightarrow} \cgamma{\gtotalc}{\vindexc^*{\dtotalc}}
\end{equation}
which is equivalent to 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf}
  \sheafc_{\vindexc^*}: \mathcal{\gbasec^{\textcolor{base}{op}}} \textcolor{sheaf}{\rightarrow} \setc
\end{equation}

@@

\begin{equation}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc", Rightarrow, shorten=1.25em, color=artist] & \\
\mathcal{\gbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\vindexc_*}(\dtotalc)", bend left, color=sheaf] \arrow[rr, "\sheafc_{\vartistc}(\gtotalc)"', bend right, color=sheaf] &  & {\setc}\\
    & {} &                            
\end{tikzcd}
\end{equation}

@@

which means that the artist, pulled back through $\vindex^*$ is a map of sections 
\begin{equation}
  \label{eq:artist:section_map}
  \vartistc_{\vindexc^*}: \dsectionc \textcolor{artist}{\mapsto}\gsectionc
\end{equation}
such that for every dataset, the artists constructs a corresponding graphic generating function. Besides preserving inclusions, as described in \autoref{eq:artist:inclusion_morphisms}, the artist function is constructed such that transformations on $\dsection$ and $\gsection$ are equivariant with respect to the morphism between data sheaf functors $\dfunc$ which was introduced in \autoref{eq:artist:morphism-of-sheaf-data}.

\subsection{Equivariance}

>>>>

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{pullback.png}
  \label{fig:artist:pushforward_xi}
  \caption{The map $\vindex^*$ is a map from a repetition of the 1D fiber over every point $\dbasepoint \in \dbase$ in data space, turning the fiber into a 2D plane of repeating values over the corresponding region $\dbasepoint = \vindex(\gbasepoint)$ in the graphic space \gbase. }
\end{figure}
Since there is a mapping from the graphic space to the total bundle $\dsection \circ \vindex: \gbase \rightarrow \dtotal$, the mapping $\vindex$ can be pulled through the composition such that there is a map $\vindex^*$ between a total space over graphics $\vindex^*\dtotal$ and its equivalent space over data $\dtotal$.  As illustrated in the example given in \autoref{fig:artist:pushforward_xi}, a bundle $\dtotal$ over a point $\dbasepoint \in \dbase$ is pulled back through \vindex\ \cite{nlab:pullback_bundle} such that it is copied over every point in the corresponding region in graphic space $\vindex(\gbasepoint) = \dbasepoint, \gbasepoint \subset \gbase$. The pullback $\vindex^*$ can then be composed with the elements of the set of sections 
\begin{equation}
  \label{eq:artist:data_gamma_pullback}
 \cgamma{\dbasec}{\dtotalc} \textcolor{artist}{\xrightarrow{\vindex^*}} \cgamma{\gbasec}{\vindexc^*\dtotalc}
\end{equation}
to generate a set of equivalent sections over the graphic $\Gamma(\gtotal, \vindex^*{\dtotal})$. As a consequence of \autoref{eq:artist:data_gamma_pullback}, there exists a data sheaf over graphic space 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf_gamma}
\sheafc_{\vindexc^*}(\dtotalc): \mathcal{\gbasec^{\textcolor{base}{op}}} \textcolor{sheaf}{\rightarrow} \cgamma{\gbasec}{\vindexc^*{\dtotalc}}
\end{equation}
which is equivalent to 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf}
  \sheafc_{\vindexc^*}: \mathcal{\gbasec^{\textcolor{base}{op}}} \textcolor{sheaf}{\rightarrow} \setc
\end{equation}

@@

\begin{equation}
  \label{eq:artist:natural-transform-diagram}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc", Rightarrow, shorten <=1.35em,  shorten >=1.25em, color=artist] & \\
\mathcal{\gbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\vindexc_*}(\dtotalc)", bend left, color=sheaf] \arrow[rr, "\sheafc_{\vartistc}(\gtotalc)"', bend right, color=sheaf] &  & {\setc}\\
    & {} &                            
\end{tikzcd}
\end{equation}

@@

which means that the artist can be pulled back through $\vindex^*$\footnote{Defintion 3.68 in Seven Sketches in Compositionality by Fong and Spivak}
\begin{equation}
  \begin{tikzcd}
    &                                                                                                                                                         & {} \arrow[dd, "\vartistc" description, Rightarrow, shorten <=1.35em,  shorten >=1.25em, color=artist] &       \\
\mathcal{\dbasec}^{\textcolor{base}{op}} \arrow[r, "\vindexc^*", color=artist] & \mathcal{\gbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\vindex^*}(\dtotalc)", bend left, color=sheaf] \arrow[rr, "\sheaf_{\vartistc}(\gtotalc)"', bend right, color=sheaf] &                                                    & \setc \\
    &                                                                                                                                                         & {}                                                 &      
\end{tikzcd}
\end{equation}
such that the artist can be constructed over data space 
\begin{equation}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc_{\vindexc^*}" description, Rightarrow, shorten <=1.35em,  shorten >=1.25em,, color=artist] &       \\
\mathcal{\dbasec}^{\textcolor{base}{op}} \arrow[rr, "\sheafc_{\vindexc^*}(\dtotalc)\circ\vindexc^* = \sheafc(\dtotalc)", bend left, color=sheaf] \arrow[rr, "\sheafc_{\vartistc}(\gtotalc)"', bend right, color=sheaf] &                                                                 & \setc \\
    & {}                                                              &      
\end{tikzcd}
\end{equation}

which in turn provides a way to construct the artist as a map from data section in data space to corresponding graphic section
\begin{equation}
  \label{eq:artist:section_map}
  \vartistc_{\vindexc^*}: \dsectionc \textcolor{artist}{\mapsto}\gsectionc
\end{equation}
such that for every dataset, the artists constructs a corresponding graphic generating function. 
\note{maybe mention here Munzner, Zeminsky, and the other dude on glyphs map back to data}
\note{possibly more here as this is the type signature of the thing we implement}

\subsection{Equivariance}
Besides preserving inclusions, as described in \autoref{eq:artist:inclusion_morphisms}, the artist function is constructed such that transformations on $\dsection$ and $\gsection$ are equivariant with respect to the morphism between data sheaf functors $\dfunc$ which was introduced in \autoref{eq:artist:morphism-of-sheaf-data}.
